---
title: "Social Network Analysis in R"
author: "Huy Doan"
date: "2023-09-10"
output: pdf_document
---
---
title: Social Network Analysis
output: html_document
---

# Social Network Analysis

## Creating a Basic Undirected Graph

```{r}
library(igraph)

# Create a basic undirected graph
g <- graph(c(1, 2, 2, 3, 3, 4, 4, 1), directed = FALSE, n = 7)
plot(g, vertex.color = "green", vertex.size = 40, edge.color = 'red')

```

#3 Direction of Relationships

```{r}
# Create a directed graph to represent relationships
g1 <- graph(c("Amy", "Ram", "Ram", "Li", "Li", "Amy", "Amy", "Li", "Kate", "Li"), directed = TRUE)
plot(g1, vertex.color = "green", vertex.size = 40, edge.color = "red")

```


#Network Measures
```{r}
# Calculate degrees
degree(g1, mode = 'all')  # Number of all in and out degrees
degree(g1, mode = 'in')   # Number of "in" degrees
degree(g1, mode = 'out')  # Number of "out" degrees

# Calculate network measures
diameter(g1, directed = FALSE, weights = NA)
edge_density(g1, loops = FALSE)
ecount(g1) / (vcount(g1) * (vcount(g1) - 1))
reciprocity(g1)
closeness(g1, mode = 'all', weights = NA)
betweenness(g1, directed = TRUE, weights = NA)
edge_betweenness(g1, directed = TRUE, weights = NA)
```
# Read Data File
```{r}

# Define the file path
file_path <- "C:/Users/Admin/Desktop/networkdata.csv"

# Read the CSV file into a data frame
data <- read.csv(file_path)
y <- data.frame(data$first, data$second)


```

#Create a Network
```{r}
# Create a directed graph 'net' from a data frame 'y'
net <- graph.data.frame(y, directed = TRUE)

# Get the vertices (nodes) of the graph 'net' and store them in a variable
vertices <- V(net)

# Get the edges of the graph 'net' and store them in a variable
edges <- E(net)

# Set the labels of vertices in 'net' to match their 'name' attribute
V(net)$label <- V(net)$name

# Calculate and store the degree (number of incident edges) of each vertex in 'net'
V(net)$degree <- degree(net)

plot(net)

```
#Histogram of Node Degree

```{R}

# Create a histogram of node degree
hist(V(net)$degree, col = 'green', main = 'Histogram of Node Degree', ylab = 'Frequency', xlab = 'Degree of Vertices')

```
#Network Diagram
```{R}

# Plot the network graph with specified visual attributes
set.seed(222)
plot(
  net,
  vertex.color = 'green',
  edge.arrow.size = 0.1,
  vertex.label.cex = 0.8
)

# Highlighting degrees & layouts:
plot(
  net,
  vertex.color = rainbow(52),
  vertex.size = V(net)$degree * 0.4,
  edge.arrow.size = 0.1,
  layout = layout.fruchterman.reingold
)

plot(
  net,
  vertex.color = rainbow(52),
  vertex.size = V(net)$degree * 0.4,
  edge.arrow.size = 0.1,
  layout = layout.graphopt
)

plot(
  net,
  vertex.color = rainbow(52),
  vertex.size = V(net)$degree * 0.4,
  edge.arrow.size = 0.1,
  layout = layout.kamada.kawai
)


```
#Hubs And Authorities:
#Authority:
Authority scores represent the importance or authority of nodes in the network.
High authority scores indicate that a node is considered authoritative or trusted in the network.
Nodes with high authority scores tend to be connected to by other nodes in the network, which gives them credibility.
In the provided results, the authority scores for each node are listed. For example, the node with label "CA" has an authority score of 1.0, indicating that it is highly authoritative in the network.


#Hubs:
Hub scores represent the importance of nodes in directing or pointing to other nodes in the network.
High hub scores indicate that a node is an important hub, meaning it points to other authoritative nodes.
Nodes with high hub scores tend to connect to highly authoritative nodes, serving as intermediaries.
In the provided results, the hub scores for each node are listed. For example, the node with label "CC" has a hub score of 1.0, indicating that it is a significant hub in the network.


```{r}
# Calculate hub scores
hs <- hub_score(net)$vector

# Calculate authority scores
as <- authority_score(net)$vector


par(mfrow=c(1,2))
set.seed(123)
plot(net, vertex.size=hs*30, main='Hubs', vertex.color = rainbow(52), edge.arrow.size=0.1, layout=layout.kamada.kawai)
#CE maximum outgoing links -- CB 2nd biggest -- on the outskirt not many outgoing links

set.seed(123)
plot(net, vertex.size=as*30, main='Authorities', vertex.color = rainbow(52), edge.arrow.size=0.1, layout=layout.kamada.kawai)
par(mfrow=c(1,1))
hs
as
```
#Community Detection:
```{r}
net<-graph.data.frame(y,directed = F)
cnet<-cluster_edge_betweenness(net)
plot(cnet, net, vertex.size = 10, vertex.label.cex = 0.8)


```























































